\emph{icepack}: a novel glacier flow modeling package

### 2020-11-11 icepack.tex
Add velocity error estimate from measures
Describe Glen flow law

\textcolor{red}{Should Glen's flow law be mentioned or written somewhere?}

@@

We used the InSAR phase-based ice velocity map from \citet{mouginot2019continent}.
This dataset has nominal errors over the Larsen Ice Shelf between \textcolor{red}{find it}.
We used the recently-released BedMachine map of the thickness of Antarctica \citep{morlighem2019deep}.
This data product improves on existing thickness maps for the continent by using the mass conservation law, together with measurements of the velocity, surface elevation, and surface mass balance, to improve thickness estimates where few measurements are available.

>>>>

All the momentum transport models inherit a fundamental nonlinearity in the mechanics of ice flow.
For a Newtonian viscous fluid, the stress tensor $\tau$ and the strain rate tensor $\dot\varepsilon$ are linearly proportional to each other.
Glaciers, however, have a nonlinear constitutive relation:
\begin{equation}
    \dot\varepsilon = A|\tau|^{n - 1}\tau
\end{equation}
where $A$ is the \emph{fluidity} and $n$ is the \emph{Glen flow law exponent} \citep{cuffey2010physics}.
The most commonly-used value of the flow law exponent is $n \approx 3$ as determined from laboratory experiments.

@@

We used the InSAR phase-based ice velocity map from \citet{mouginot2019continent}.
This dataset has nominal errors over the Larsen Ice Shelf on the order 1 -- 7 meters per year.
We used the recently-released BedMachine map of the thickness of Antarctica \citep{morlighem2019deep}.
This data product improves on existing thickness maps for the continent by using the mass conservation law, together with measurements of the velocity, surface elevation, and surface mass balance, to improve thickness estimates where few measurements are available.
